The Bug Catalog of the Maven Ecosystem

### 2014-02-20 docs/msr.tex
updated section 2; merged new text with the previous one

The initial snapshot of the repository was obtained in January 2012 and those experinment took
place in the end of 2012. In the meantime, several versions were released for some of the selected project.
We added them in an incremental way, using the following methodology; we implemented a script that cross-checked 
all the local versions of the project with those online;\footnote{\url{http://mirrors.ibiblio.org/maven2/}} and downloaded
the missing ones.

The whole process produced a file list with all the valid {\sc jar} files for our experinment. Each file on the list were uploaded as a separate task in the task queue (Figure~XXX). Concurent workers processed each task and submitted the results to the mongo database.

@@

The sanitisation process was consisted of four iterations, until all our scripts indicate that our data was correct.

In particular, we obtained a snapshot (January 2012) of
the repository and handled it locally to retrieve a list of all
the names of the Java project versions that existed in it.
The statistic measurements concerning the repository can be seen in 
Table~\ref{tbl:repository}.

With the {\sc jar} list at hand, we created a series of processing tasks
and added them to a task queue mechanism (a Rabbit{\sc mq} message
broker). Then we executed twenty five workers (custom Python scripts)
that checked out tasks from the queue, processed each project version
and stored the results to the data
repository (a Mongo{\sc db} database system).

A typical processing cycle of a worker included the following steps: after
the worker spawned, it requested a task from the queue. This task contained
the {\sc jar} name, which was typically a project version that was downloaded locally.
First, specific {\sc jar} metadata were calculated and stored
(see Table~\ref{tbl:metadata-description}).
Such metadata included
its size, its dependencies, and a number that
represented the ordinal version number
of the release. This number was derived from an {\sc xml} file that
accompanies every project in the Maven repository called {\it
maven-metadata.xml}. Then, FindBugs was invoked by the worker and its results were
also stored in the data repository. 
FindBugs separates software bugs into nine
categories\footnote{\url{http://findbugs.sourceforge.net/bugDescriptions.html}}
(including {\it Bad Practice}, {\it Security}, {\it Performance} and others)
and reports bug collections that include all the bugs discovered in a
{\sc jar} file. For every registered bug, there are numerous accompanying features
like the class, the method and the line that the bug was found.
Its results, also include additional information like
the number of classes included in the examined {\sc jar}
and others.
When the task was completed the queue
was notified and the next task was requested.

A threat to the internal
validity of our experiment could be the false
alarms of the FindBugs tool~\cite{AP10, HP04}.
Specifically, reported security bugs may not
be applicable to an application's typical use context.
For instance, FindBugs could report an {\sc sql}
injection vulnerability~\cite{RL12}
in an application that receives no external input.
In this particular context, this would be a false
positive alarm.

>>>>

The initial snapshot of the repository was obtained in January 2012 and those experinment took
place in the end of 2012. The statistic measurements concerning the repository can be seen in 
Table~\ref{tbl:repository}. In the meantime, several versions were released for some of the selected project.
We added them in an incremental way, using the following methodology; we implemented a script that cross-checked 
all the local versions of the project with those online;\footnote{\url{http://mirrors.ibiblio.org/maven2/}} and downloaded
the missing ones.

The whole process produced a file list with all the valid {\sc jar} files for our experinment. Each file on the list were uploaded as a separate task in the task queue (Figure~XXX). Concurent workers processed each task and submitted the results to the mongo database. A typical processing cycle of a worker included the following steps: after
the worker spawned, it requested a task from the queue. This task contained
the {\sc jar} name, which was typically a project version that was downloaded locally.
First, specific {\sc jar} metadata were calculated and stored
(see Table~\ref{tbl:metadata-description}).
Such metadata included
its size, its dependencies, and a number that
represented the ordinal version number
of the release. This number was derived from an {\sc xml} file that
accompanies every project in the Maven repository called {\it
maven-metadata.xml}. Then, FindBugs was invoked by the worker and its results were
also stored in the data repository. 
FindBugs separates software bugs into nine
categories\footnote{\url{http://findbugs.sourceforge.net/bugDescriptions.html}}
(including {\it Bad Practice}, {\it Security}, {\it Performance} and others)
and reports bug collections that include all the bugs discovered in a
{\sc jar} file. For every registered bug, there are numerous accompanying features
like the class, the method and the line that the bug was found.
Its results, also include additional information like
the number of classes included in the examined {\sc jar}
and others.

@@

The sanitisation process was consisted of four iterations, until all our scripts indicate that our data was correct. A threat to the internal
validity of our experiment could be the false
alarms of the FindBugs tool~\cite{AP10, HP04}.
Specifically, reported security bugs may not
be applicable to an application's typical use context.
For instance, FindBugs could report an {\sc sql}
injection vulnerability~\cite{RL12}
in an application that receives no external input.
In this particular context, this would be a false
positive alarm.
